About

### 2024-11-29 about.qmd
Improve license wording
Improve license statement on about page

If not indicated otherwise, this tutorial is licensed under [CC\ BY\ 4.0](https://creativecommons.org/licenses/by/4.0/). None of the discussion in this tutorial constitutes legal advice.

Any screenshots of [RStudio](https://github.com/rstudio/rstudio) are released under the [GNU Affero General Public License v3](https://www.gnu.org/licenses/gpl-3.0.html).

@@

You should have received a copy of the GNU Affero General Public License along with this program.  If not, see <https://www.gnu.org/licenses/>.
```

>>>>

Except where noted otherwise, the material in this tutorial is licensed under [CC\ BY\ 4.0](https://creativecommons.org/licenses/by/4.0/). None of the discussion in this tutorial constitutes legal advice.

The screenshots of the [RStudio IDE](https://github.com/rstudio/rstudio) are available under the [GNU Affero General Public License v3](https://www.gnu.org/licenses/gpl-3.0.html).

::: {.nte-agplv3 .callout-note collapse="true"}
### GNU Affero General Public License v3

@@

You should have received a copy of the GNU Affero General Public License along with this program.  If not, see <https://www.gnu.org/licenses/>.
```
:::
